The role of cognateness in native spoken word recognition

### 2024-10-17 manuscript/manuscript.qmd
Fix table of surprises

```{r tbl-surprises}
#| label: tbl-surprises
#| tbl-cap: "List of items with unexpectedly high accuracy: the Levenshtein similarityscore betwen the presented word (in Catalan or Spanish) and their correct Enlgish translation is zero, but participants, who are reportedly unfamiliar with the presented language, were on average >10% likely to guess the correct translation."
tbl_data <- list(
  "Experiment 1" = dataset_1,
  "Experiment 2" = dataset_2
) |>
  bind_rows(.id = "exp") |>
  mutate(translation = paste0())
  summarise(
    n = n(),
    correct = sum(correct),
    .by = c(exp, group, lv, translation)
  ) |>
  mutate(
    accuracy = prop_adj(correct, n),
    accuracy_se = prop_adj_se(correct, n)
  ) |>
  dplyr::filter(lv == 0, accuracy >= 0.1) |>
  select(exp, translation, group, accuracy, accuracy_se) |>
  arrange(exp, group, desc(accuracy))

tbl_data |>
  select(translation, accuracy, accuracy_se) |> 
  mutate(accuracy = round(accuracy * 100, 2),
         accuracy_se = round(accuracy_se * 100, 2)) |> 
  set_names(c("Translation", "Accuracy (%)", "SE")) |> 
  tt() |> 
  group_tt(i = list(
    "Experiment 1 (cat-ENG)" = 5,
    "Experiment 2 (spa-ENG)" = 21,
    "Experiment 3 (cat-SPA)" = 26))
```

>>>>

```{r tbl-surprises}
#| label: tbl-surprises
#| tbl-cap: "List of items with unexpectedly high accuracy: the Levenshtein similarityscore betwen the presented word (in Catalan or Spanish) and their correct English translation is zero, but participants, who are reportedly unfamiliar with the presented language, were on average >10% likely to guess the correct translation."
tbl_data <- list(
  "Experiment 1" = dataset_1,
  "Experiment 2" = dataset_2
) |>
  bind_rows(.id = "exp") |>
  mutate(
    translation = paste0(word_1, " - ",  word_2),
    xsampa = paste0("/", sampa_1, "/ - /", sampa_2, "/")
  ) |> 
  summarise(
    n = n(),
    correct = sum(correct),
    .by = c(exp, group, lv, translation, xsampa)
  ) |>
  mutate(
    accuracy = prop_adj(correct, n),
    accuracy_se = prop_adj_se(correct, n)
  ) |>
  dplyr::filter(lv == 0, accuracy >= 0.1) |>
  select(exp, translation, xsampa, group, accuracy, accuracy_se) |>
  arrange(exp, group, desc(accuracy)) |> 
  select(translation, xsampa, accuracy, accuracy_se) |> 
  mutate(accuracy = round(accuracy * 100, 2),
         accuracy_se = round(accuracy_se * 100, 2))

names(tbl_data) <- c("Translation", "X-SAMPA", "Accuracy (\\%)", "SE")

tt(tbl_data) |> 
  group_tt(i = list(
    "Experiment 1 (cat-ENG)" = 1,
    "Experiment 2 (spa-ENG)" = 6,
    "Experiment 3 (cat-SPA)" = 22)) |> 
  style_tt(i = 0, bold = TRUE, line = "tb") |> 
  style_tt(i = 1, bold = TRUE, line = "b") |> 
  style_tt(i = 7, bold = TRUE, line = "tb") |> 
  style_tt(i = 24, bold = TRUE, line = "tb")

### 2024-10-17 manuscript/manuscript.tex
Fix table of surprises

\caption{\label{tbl-surprises}List of items with unexpectedly high
accuracy: the Levenshtein similarityscore betwen the presented word (in
Catalan or Spanish) and their correct Enlgish translation is zero, but
participants, who are reportedly unfamiliar with the presented language,
were on average \textgreater10\% likely to guess the correct
translation.}

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]},
cell{6}{1}={c=3}{},cell{23}{1}={c=3}{},cell{29}{1}={c=3}{},
cell{2}{1}={preto={\hspace{1em}}},
cell{3}{1}={preto={\hspace{1em}}},
cell{4}{1}={preto={\hspace{1em}}},
cell{5}{1}={preto={\hspace{1em}}},
cell{7}{1}={preto={\hspace{1em}}},
cell{8}{1}={preto={\hspace{1em}}},
cell{9}{1}={preto={\hspace{1em}}},
cell{10}{1}={preto={\hspace{1em}}},
cell{11}{1}={preto={\hspace{1em}}},
cell{12}{1}={preto={\hspace{1em}}},
cell{13}{1}={preto={\hspace{1em}}},
cell{14}{1}={preto={\hspace{1em}}},
cell{15}{1}={preto={\hspace{1em}}},
cell{16}{1}={preto={\hspace{1em}}},
cell{17}{1}={preto={\hspace{1em}}},
cell{18}{1}={preto={\hspace{1em}}},
cell{19}{1}={preto={\hspace{1em}}},
cell{20}{1}={preto={\hspace{1em}}},
cell{21}{1}={preto={\hspace{1em}}},
cell{22}{1}={preto={\hspace{1em}}},
cell{24}{1}={preto={\hspace{1em}}},
cell{25}{1}={preto={\hspace{1em}}},
cell{26}{1}={preto={\hspace{1em}}},
cell{27}{1}={preto={\hspace{1em}}},
cell{28}{1}={preto={\hspace{1em}}},
cell{30}{1}={preto={\hspace{1em}}},
cell{31}{1}={preto={\hspace{1em}}},
}                     %% tabularray inner close
\toprule
Translation & Accuracy (%) & SE \\ \midrule %% TinyTableHeader
cavall /kəβaʎ/ - horse /hɔs/             & 17.14 & 6.37 \\
llibre /ʎiβɾə/ - book /bʊk/              & 17.14 & 6.37 \\
camisa /kəmizə/ - shirt /ʃɜt/            & 16.67 & 6.21 \\
poma /poma/ - apple /æpl/                & 16.67 & 6.21 \\
Experiment 1 (cat-ENG) && \\
cama /kamə/ - leg /lɛg/                  & 11.11 & 5.24 \\
pantalón /paŋtalon/ - trousers /traʊzəz/ & 77.42 & 7.51 \\
naranja /naɾaŋxa/ - orange /ɒrɪnʤ/       & 41.94 & 8.86 \\
leche /leʧe/ - milk /mɪlk/               & 35.48 & 8.59 \\
toro /toɾo/ - bull /bʊl/                 & 33.33 & 8.61 \\
libro /liβɾo/ - book /bʊk/               & 30.00 & 8.37 \\
cebra /θebɾa/ - zebra /zibrə/            & 29.03 & 8.15 \\
pan /pan/ - bread /brɛd/                 & 29.03 & 8.15 \\
pollo /poʎo/ - chicken /ʧɪkɪn/           & 26.67 & 8.07 \\
jirafa /xiɾafa/ - giraffe /ʤɪrɑf/        & 20.69 & 7.52 \\
perro /pero/ - dog /dɒɡ/                 & 16.13 & 6.61 \\
pluma /pluma/ - feather /fɛðə/           & 16.13 & 6.61 \\
puerta /pwerta/ - door /dɔ/              & 16.13 & 6.61 \\
pie /pje/ - foot /fʊt/                   & 12.90 & 6.02 \\
caballo /kaβaʎo/ - horse /hɔs/           & 10.34 & 5.66 \\
bocadillo /bokadiʎo/ - sandwich /sænwɪʤ/ & 10.00 & 5.48 \\
Experiment 2 (spa-ENG) && \\
globo /ɡloβo/ - balloon /bəlun/          & 10.00 & 5.48 \\
fulla /fuʎə/ - hoja /oxa/                & 30.43 & 9.59 \\
ull /uʎ/ - ojo /oxo/                     & 21.74 & 8.60 \\
got /gɔt/ - vaso /baso/                  & 20.00 & 8.00 \\
entrepà /entɾəpa/ - bocadillo /bokadiʎo/ & 13.04 & 7.02 \\
Experiment 3 (cat-SPA) && \\
mirall /miɾaʎ/ - espejo /espexo/         & 12.50 & 6.75 \\
\bottomrule
\end{tblr}

>>>>

\caption{\label{tbl-surprises}List of items with unexpectedly high
accuracy: the Levenshtein similarityscore betwen the presented word (in
Catalan or Spanish) and their correct English translation is zero, but
participants, who are reportedly unfamiliar with the presented language,
were on average \textgreater10\% likely to guess the correct
translation.}

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]},
cell{2}{1}={c=4}{},cell{8}{1}={c=4}{},cell{25}{1}={c=4}{},
cell{3}{1}={preto={\hspace{1em}}},
cell{4}{1}={preto={\hspace{1em}}},
cell{5}{1}={preto={\hspace{1em}}},
cell{6}{1}={preto={\hspace{1em}}},
cell{7}{1}={preto={\hspace{1em}}},
cell{9}{1}={preto={\hspace{1em}}},
cell{10}{1}={preto={\hspace{1em}}},
cell{11}{1}={preto={\hspace{1em}}},
cell{12}{1}={preto={\hspace{1em}}},
cell{13}{1}={preto={\hspace{1em}}},
cell{14}{1}={preto={\hspace{1em}}},
cell{15}{1}={preto={\hspace{1em}}},
cell{16}{1}={preto={\hspace{1em}}},
cell{17}{1}={preto={\hspace{1em}}},
cell{18}{1}={preto={\hspace{1em}}},
cell{19}{1}={preto={\hspace{1em}}},
cell{20}{1}={preto={\hspace{1em}}},
cell{21}{1}={preto={\hspace{1em}}},
cell{22}{1}={preto={\hspace{1em}}},
cell{23}{1}={preto={\hspace{1em}}},
cell{24}{1}={preto={\hspace{1em}}},
cell{26}{1}={preto={\hspace{1em}}},
cell{27}{1}={preto={\hspace{1em}}},
cell{28}{1}={preto={\hspace{1em}}},
cell{29}{1}={preto={\hspace{1em}}},
cell{30}{1}={preto={\hspace{1em}}},
cell{31}{1}={preto={\hspace{1em}}},
row{1}={,cmd=\bfseries,},
hline{1,2}={1,2,3,4}{solid, 0.1em, black},
row{2}={,cmd=\bfseries,},
hline{3}={1,2,3,4}{solid, 0.1em, black},
row{8}={,cmd=\bfseries,},
hline{8,9}={1,2,3,4}{solid, 0.1em, black},
row{25}={,cmd=\bfseries,},
hline{25,26}={1,2,3,4}{solid, 0.1em, black},
}                     %% tabularray inner close
\toprule
Translation & X-SAMPA & Accuracy (\%) & SE \\ \midrule %% TinyTableHeader
Experiment 1 (cat-ENG) &&& \\
cavall - horse       & /k5BaL/ - /hOs/          & 17.14 & 6.37 \\
llibre - book        & /LiB45/ - /bUk/          & 17.14 & 6.37 \\
camisa - shirt       & /k5miz5/ - /S36t/        & 16.67 & 6.21 \\
poma - apple         & /poma/ - /1pl/           & 16.67 & 6.21 \\
cama - leg           & /kam5/ - /lEg/           & 11.11 & 5.24 \\
Experiment 2 (spa-ENG) &&& \\
pantalon - trousers  & /pantalon/ - /tr0aUs56z/ & 77.42 & 7.51 \\
naranja - orange     & /na4aNxa/ - /Or0I0ndZ/   & 41.94 & 8.86 \\
leche - milk         & /letSe/ - /mIlk/         & 35.48 & 8.59 \\
toro - bull          & /to4o/ - /bUl/           & 33.33 & 8.61 \\
libro - book         & /liB4o/ - /bUk/          & 30.00 & 8.37 \\
cebra - zebra        & /TeB4a/ - /zibr05/       & 29.03 & 8.15 \\
pan - bread          & /pan/ - /br0Ed/          & 29.03 & 8.15 \\
pollo - chicken      & /poLo/ - /tSIkIn/        & 26.67 & 8.07 \\
jirafa - giraffe     & /xi4afa/ - /dZI0r01f/    & 20.69 & 7.52 \\
perro - dog          & /pErro/ - /dAg/          & 16.13 & 6.61 \\
pluma - feather      & /pluma/ - /fED56/        & 16.13 & 6.61 \\
puerta - door        & /pwE4ta/ - /dor/         & 16.13 & 6.61 \\
pie - foot           & /pje/ - /fUt/            & 12.90 & 6.02 \\
caballo - horse      & /kaBaLo/ - /hors/        & 10.34 & 5.66 \\
bocadillo - sandwich & /bokaDiLo/ - /s1ndwItS/  & 10.00 & 5.48 \\
globo - balloon      & /gloBo/ - /b5lun/        & 10.00 & 5.48 \\
Experiment 3 (cat-SPA) &&& \\
fulla - hoja         & /fuL5/ - /oxa/           & 30.43 & 9.59 \\
ull - ojo            & /uL/ - /oxo/             & 21.74 & 8.60 \\
got - vaso           & /gOt/ - /baso/           & 20.00 & 8.00 \\
entrepa - bocadillo  & /ent45pa/ - /bokaDiLo/   & 13.04 & 7.02 \\
mirall - espejo      & /mi4aL/ - /espexo/       & 12.50 & 6.75 \\
\bottomrule
\end{tblr}
